Merging Datasets Through Deep learning

### 2018-09-02 paper2018/evaluation.tex
hacked tables

\begin{table*}[ht]
\caption{Precision and Recall for people and companies by loss functions}
\label{Evaluation}
\begin{tabular}{l|l|r|r|r|}
\hline
Entity Type & Loss Function & Recall & Precision@1 & Precision \\
\hline
\multirow{4}{*}{People} & Adapted loss & .81 & .81 & .63 \\
\hline
& Triplet loss & .74 & .84 & .55 \\
\hline
& Improved loss & .71 & .52 & .45 \\
\hline
& Angular loss & .04 & .09 & .02 \\
\hline
\multirow{4}{*}{Companies} & Adapted loss & .72 & .73 & .64 \\
& Triplet loss & .75 & .76 & .67 \\
\hline
& Improved loss & .74 & .72 & .64 \\
\hline
& Angular loss & NA & NA & NA \\
\hline
\end{tabular}
\end{table*}

\begin{table*}[ht]
\caption{Distance estimates for people and companies after training}
\label{Evaluation}
\begin{tabular}{l|l|r|r|r|r|}
\hline
Entity Type & Loss Function & Mean Pos & Std Pos & Mean Neg & Std Neg \\
\hline
\multirow{4}{*}{People} & Adapted loss & 1.59 & 4.04 & 2.44 & 2.45 \\
\hline
& Triplet loss & .46 & .18 & .55 & .10 \\
\hline
& Improved loss & .15 & .38 & .21 & .18 \\
\hline
& Angular loss & .51 & .25 & .06 & .02 \\
\hline
\multirow{4}{*}{Companies} & Adapted loss & 2.38 & 3.77 & 3.23 & 1.71 \\
\hline
& Triplet loss & .39 & .28 & .55 & .09 \\
\hline
& Improved loss & .32 & .50 & .42 & 0.19 \\
\hline
& Angular loss & NA & NA & NA & NA \\
\hline
\end{tabular}
\end{table*}

>>>>

\begin{table}[ht]
\caption{Precision and Recall by loss functions}
\label{Evaluation}
\begin{center}
\begin{tabular}{l|l|r|r|r|}
\hline
Entities & Loss & Recall & \multicolumn{2}{|c|}{Precision} \\
 & & & @1 & All \\
\hline
\multirow{4}{*}{People} & Adapted & .81 & .81 & .63 \\
\cline{2-5}
& Triplet & .74 & .84 & .55 \\
\cline{2-5}
& Improved & .71 & .52 & .45 \\
\cline{2-5}
& Angular & .04 & .09 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & .72 & .73 & .64 \\
\cline{2-5}
& Triplet & .75 & .76 & .67 \\
\cline{2-5}
& Improved & .74 & .72 & .64 \\
\cline{2-5}
& Angular & NA & NA & NA \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[ht]
\caption{Distance estimates after training}
\label{Evaluation}
\begin{center}
\begin{tabular}{l|l|r|r|r|r|}
\hline
Entities & Loss & \multicolumn{2}{|c|}{Pos} & \multicolumn{2}{|c}{Neg} \\
& & Mean & Std & Mean & Std \\
\hline
\multirow{4}{*}{People} & Adapted & 1.59 & 4.04 & 2.44 & 2.45 \\
\cline{2-6}
& Triplet & .46 & .18 & .55 & .10 \\
\cline{2-6}
& Improved & .15 & .38 & .21 & .18 \\
\cline{2-6}
& Angular & .51 & .25 & .06 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & 2.38 & 3.77 & 3.23 & 1.71 \\
\cline{2-6}
& Triplet & .39 & .28 & .55 & .09 \\
\cline{2-6}
& Improved & .32 & .50 & .42 & 0.19 \\
\cline{2-6}
& Angular & NA & NA & NA & NA \\
\hline
\end{tabular}
\end{center}
\end{table}
